---
title: "Haven Project"
author: "Emily Beasley"
date: "11/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#####to install the haven package, you can use regular install.packages _or_ you can just install tidyverse

```{r}
#install.packages("haven")

library(haven)

```

#### for the SAS application, we'll read in its files and write them out like so:

```{r}
# SAS
#read_sas("mtcars.sas7bdat")
#write_sas(mtcars, "mtcars.sas7bdat")
```

#### for the SPSS application (the very application i actually use for doing research with UROC), we'll read in its files and write them out like so:

```{r}
# SPSS
#read_sav("mtcars.sav")
#write_sav(mtcars, "mtcars.sav")
```

####for the SAS application, we'll read in its files and write them out like so:

```{r}
# Stata
#read_dta("mtcars.dta")
#write_dta(mtcars, "mtcars.dta")
```

#### some functions to use:

```{r}
#the LABELLED function assigns text labels to specific values

#labelled(x, labels, label = NULL)

# x is a vector to label. Must be either numeric (integer or double) or character.

#labels is a named vector or NULL. The vector should be the same type as x. Unlike factors, labels don't need to be exhaustive: only a fraction of the values might be labelled

# and label is a short, human-readable description of the vector

```

```{r}
#as_factor converts input to a FACTOR

#as_factor(x, ..., only_labelled = TRUE)

#  we use x to coerce to a factor and
# other arguments passed down to method.

# only_labelled wasnt very clear on its purpose but we use that for maybe applying to labelled columns?

#levels is how to create the levels of the generated factor:

# - "default": uses labels where available, otherwise the values. Labels are sorted by value.

# - "both": like "default", but pastes together the level and value

# - "label": use only the labels; unlabelled values become NA

# - "values: use only the values ordered... if TRUE create an ordered (ordinal) factor, if FALSE (the default) create a regular (nominal) factor.
```

```{r}
#zap_empty function converts strings into missing values

#zap_empty(x)

#x being a CHARACTER vector

```




