---
title: "Likert Package"
output:
  word_document: default
  html_notebook: default
---

Install the packages "psych" and "likert

```{r}
if(!require(psych)){install.packages("psych")}
if(!require(likert)){install.packages("likert")}
library("psych")
library("likert")

```

##  ------------------- Setting up... -------------------

```{r}
options(digits=2)

require(likert)
data(pisaitems)
```

"pisaitems":
Programme of International Student Assessment
North American (i.e. Canada, Mexico, and United States) results from the 2009 Programme of International Student Assessment (PISA) as provided by the Organization for Economic Co-operation and Development (OECD). See http://www.pisa.oecd.org/ for more information including the code book.

```{r}
##### Item 24: Reading Attitudes
items24 <- pisaitems[,substr(names(pisaitems), 1,5) == 'ST24Q']
head(items24); ncol(items24)

names(items24) <- c(
			ST24Q01="I read only if I have to.",
			ST24Q02="Reading is one of my favorite hobbies.",
			ST24Q03="I like talking about books with other people.",
			ST24Q04="I find it hard to finish books.",
			ST24Q05="I feel happy if I receive a book as a present.",
			ST24Q06="For me, reading is a waste of time.",
			ST24Q07="I enjoy going to a bookstore or a library.",
			ST24Q08="I read only to get information that I need.",
			ST24Q09="I cannot sit still and read for more than a few minutes.",
			ST24Q10="I like to express my opinions about books I have read.",
			ST24Q11="I like to exchange books with my friends.")
str(items24)
l24 <- likert(items24)

```


#  ------------------- 1: Summarize -------------------

```{r}
summary(l24)
```

#  ------------------- 2: Plots -------------------
```{r}
plot(l24)
plot(l24, ordered=FALSE, ______________=names(items24)) 
plot(l24, center=2.5, wrap=30)

#code to change colors
#plot(l24, colors=c('orange','darkorange','darkblue','blue'))

```


#  ------------------- 3: Heat Plot -------------------
```{r}
plot(l24, type = 'heat', wrap=30, text.size=4, digits = 0) + ggtitle('My title')


```


#  ------------------- 4: Reversing Levels -------------------
```{r}
# Reverse the levels
items24.reverse <- reverse.levels(items24)
l24.reverse <- likert(items24.reverse)
print(l24.reverse)
plot(l24)
plot(l24.reverse)

```


#  ------------------- 5: Viewing one variable -------------------
```{r}
## With only one varaible
lone <- likert(items24[___ drop=FALSE])
plot(lone)

loneg <- likert(items24[___ drop=FALSE], _________=pisaitems$CNT)
plot(loneg)
```


source: https://github.com/jbryer/likert/blob/master/demo/likert.R 







